---
title: "Spatial Data Visualization"
author: "Armando Saavedra"
date: "3/23/2020"
output:
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
---



```{css, echo=FALSE}
.fluid.row.title{
  font-size: 2.9vw
}
h1{
  font-size:1.9vw;
  margin-top: 30px!important;
  margin-bottom: 15px!important;
  padding-top: 0px!important;
  padding-bottom: 0px!important;
  font-weight: bold;
  border-bottom: solid 1px black;
}

h2{
  margin-top: 30px!important;
  margin-bottom: 15px!important;
  padding-top: 0px!important;
  padding-bottom: 0px!important;
  font-size: 22px;
  font-weight: bold
}
p{
  display: block;
  margin-block-start: 1em;
  margin-block-end: 1em;
  margin-inline-start: 0px;
  margin-inline-end: 0px;
  
}


  

```


<style>
.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
    background-color: black;
}
</style>

# Introduction

The goal of this project is to analyze spatial data summarizing the number of acidents in New york. The objective is to create a heat map where every zip code shows the number of car accidents.

The information base of this analysis comes from a dataset found in Kaggle that provides differents 


# Requiered Libraries
his is an R Markdown document. Markdown i



```{r,message=FALSE, warning=FALSE,paged.print=TRUE}
library(sf)
library(tmap)
library(leaflet)
library(ggmap)
library(dplyr)
library(stringr)
library(lubridate)
library(zoo)
library(DT)
library(data.table)
library(ggplot2)
library(ggthemes)

```
# Data

```{r,results = "hide"}
data=read.csv('C:/Users/dsaav/Documents/Projects/R/Datasets/database.csv',
              header=TRUE,stringsAsFactors = FALSE)
sum(is.na(data$ZIP.CODE))

```

# Fix Zipcodes
```{r,results = "hide"}
library(ggmap)

dset<-data[!complete.cases(data$LATITUDE), ]
sum(is.na(dset$LATITUDE))


library(googleway)


key <- "AIzaSyDqZc13hrQ7ELNTxdD3SybCSvVO0uMow90"

res <- apply(dset, 1, function(x){
  google_reverse_geocode(location = c(x["LATITUDE"], x["LONGITUDE"]),
                         key = key)})

# can then access zip and neighborhood where populated
res$postal_code
res$neighborhood

```


```{r,results = "hide"}




# data<-na.omit(data) 

# for visualization
data1<-data[,-1]
# For Integration
data2<-data[,c(5,13:19)]

# Summarize Data

zips_counts<-data2%>%
  group_by(ZIP.CODE)%>%
  summarise(no_zips=length(ZIP.CODE))%>%
  arrange(desc(no_zips))




data2<-setDT(data2)[,lapply(.SD,sum),
                    by=ZIP.CODE,.SDcols=c("PERSONS.KILLED","PEDESTRIANS.INJURED",                                                         "PEDESTRIANS.KILLED","CYCLISTS.INJURED",                                                        "CYCLISTS.KILLED","MOTORISTS.INJURED",                                                          "MOTORISTS.KILLED")]


data2<-merge(zips_counts,data2,by='ZIP.CODE')

```


# Visualization
```{r}

data1$DATE<-parse_date_time(data1$DATE, orders=c("ymd", "dmy", "mdy"))



data1$Day<- factor(day(data1$DATE))
data1$Month<-factor(month(data1$DATE))
data1$DayWeek<-factor(wday(data1$DATE))
data1$Year<-factor(year(data1$DATE))

# Visualize days
day_data <- data1 %>%
  group_by(Day) %>%
  summarize(Total = n()) 

ggplot(day_data,aes(Day,Total))+geom_bar(stat = 'identity',fill="#00526D")+
  labs(title="Accidents by Day") + 
  labs(x="Localidad")+labs(y="Mean Days")+theme_economist() +
  scale_colour_economist()

month_data <- data1 %>%
  group_by(Month) %>%
  summarize(Total = n())


dayofweek_data <- data1 %>%
  group_by(DayWeek) %>%
  summarize(Total = n()) 

year_data <- data1 %>%
  group_by(Year) %>%
  summarize(Total = n()) 


month_year_group<-data1 %>%
  group_by(Year, Month) %>%
  summarize(Total = n())



```



# Zip codes geometrics from US Census

```{r ,results = "hide"}


zipsManha<-st_read('C:/Users/dsaav/Documents/Projects/R/Datasets/acs2018_5yr_B01003_86000US10543/acs2018_5yr_B01003_86000US10543.shp')
zipsManha<-zipsManha[-1,c(1,2,5)]

library(varhandle)
zipsManha$name<-unfactor(zipsManha$name)
zipsManha$name<-as.integer(zipsManha$name)


#data_sf<-st_as_sf(data, coords=c('LONGITUDE','LATITUDE'),crs=4326,remove =FALSE )



common_zip<-union(data2$ZIP.CODE,zipsManha$name)
length(common_zip)==length(data2$ZIP.CODE)

library(tmaptools)


data_Integration<-merge(zipsManha,data2, by.x ='name',by.y='ZIP.CODE')



```

```{r,message = FALSE,warning = FALSE}
library(tmap)
library(ggmap)

ttm()
#tmap_last()
#qtm(data_Integration,fill = 'no_zips')

tm_shape(data_Integration)+tm_polygons(col = "no_zips", id = "name")

```




